This program is a toolbox to solve special versions of the Set Partitioning Problem, that is the combinatorial optimisation of a decomposable objective over a set of feasible partitions (defined according to specific algebraic structures\-: e.\-g., hierachies, sets of intervals, graphs). The objectives are mainly based on information theory, in the perspective of multilevel analysis of large-\/scale datasets, and the algorithms are based on dynamic programming. For details regarding the formal grounds of this work, please refer to\-:

Robin Lamarche-\/\-Perrin, Yves Demazeau and Jean-\/\-Marc Vincent. A Generic Set Partitioning Algorithm with Applications to Hierarchical and Ordered Sets. Technical Report 105/2014, Max-\/\-Planck-\/\-Institute for Mathematics in the Sciences, Leipzig, Germany, May 2014.

\href{http://www.mis.mpg.de/publications/preprints/2014/prepr2014-105.html}{\tt http\-://www.\-mis.\-mpg.\-de/publications/preprints/2014/prepr2014-\/105.\-html}

Copyright © 2015 Robin Lamarche-\/\-Perrin (\href{mailto:Robin.Lamarche-Perrin@lip6.fr}{\tt Robin.\-Lamarche-\/\-Perrin@lip6.\-fr})

This program is free software\-: you can redistribute it and/or modify it under the terms of the G\-N\-U General Public License as published by the Free Software Foundation, either version 3 of the License, or (at your option) any later version.

This program is distributed in the hope that it will be useful, but W\-I\-T\-H\-O\-U\-T A\-N\-Y W\-A\-R\-R\-A\-N\-T\-Y; without even the implied warranty of M\-E\-R\-C\-H\-A\-N\-T\-A\-B\-I\-L\-I\-T\-Y or F\-I\-T\-N\-E\-S\-S F\-O\-R A P\-A\-R\-T\-I\-C\-U\-L\-A\-R P\-U\-R\-P\-O\-S\-E. See the G\-N\-U General Public License for more details.

You should have received a copy of the G\-N\-U General Public License along with this program. If not, see \href{http://www.gnu.org/licenses/}{\tt http\-://www.\-gnu.\-org/licenses/}. 